Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-29 prop_iop.tex
prop_iop.tex \subsection{Between Expectation Values for Quantum Real-valued and Interval-valued Probability Measures} Updating...
prop_iop.tex \subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability Measures} Added...

The Choquet integral has many desirable properties. For example, it
has the same range as all expectation value in the core.

@@

\begin{lemma}\label{lemma:interval-expectation-value-between-classical-quantum}Adopting
the definitions in this subsection. Given a quantum IVPM~$\bar{\mu}$,
there is a classical real-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'$.\end{lemma}

@@

Notice that lemma~\ref{lemma:real-expectation-value-between-classical-quantum}
guarantees that for any $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
there exists $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that
$\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. On the other hand, for any
$\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we have
\begin{eqnarray}
 &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
\end{eqnarray}
Let $\rho=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}P_{i}^{s}$.
Then, we have 
\begin{eqnarray}
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{-}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{-}\right)=\mu'\left(\tau\left(P_{j}^{-}\right)\right)\\
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{+}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{+}\right)=\mu'\left(\tau\left(P_{j}^{+}\right)\right)
\end{eqnarray}
Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}

@@

\begin{lemma}Given a Hilbert space of $d\ge3$, when $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are real-valued probability
measures, we have $\mul=\mur=\mu_{\rho}^{\mathrm{B}}$ for some density
matrix~$\rho$. Then, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.\end{lemma}

\begin{proof}The first part of the lemma is the consequence of Gleason's
theorem directly. For the second part of the lemma \end{proof}

After we defined the expectation value, we can provide another proof
of corollary~\ref{cor:Kochen-Specker-IVPM} which doesn't refer the
Kochen-Specker theorem directly.

@@

\begin{proof}Assume there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
we will prove $\bar{\mu}$ has such bizarre properties that it cannot
exist.\end{proof}

>>>>

The Choquet integral has many desirable properties. For example, it
has the same range as all expectation value in the core, and it generalizes
the Lebesgue integral.

@@

\begin{lemma}\label{lemma:interval-expectation-value-between-classical-quantum}Adopting
the definitions in this subsection. Given a quantum IVPM~$\bar{\mu}$,
there is a classical IVPM~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'$.\end{lemma}

@@

Notice that lemma~\ref{lemma:real-expectation-value-between-classical-quantum}
guarantees that for any $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
there exists $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that
$\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. On the other hand, for any
$\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we have
\begin{eqnarray}
 &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
\end{eqnarray}
Let $\rho=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}P_{i}^{s}$.
$\rho$ is a density matrix because~\cite{544199}
\begin{eqnarray}
\Tr\left(\rho\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}\right)=1\textrm{ .}
\end{eqnarray}
Also, 
\begin{eqnarray}
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{s'}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{s'}\right)=\mu'\left(\tau\left(P_{j}^{s'}\right)\right)
\end{eqnarray}
for $s'\in\left\{ +,-\right\} $ and $1\le j\le N^{s'}$. Therefore,
$\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}

@@

\begin{lemma}\label{lemma:expectation-singleton}Given a Hilbert
space of $d\ge3$, when $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are real-valued probability
measures, we have $\mul=\mur=\mu_{\rho}^{\mathrm{B}}$ for some density
matrix~$\rho$. Then, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.\end{lemma}

\begin{proof}Adopting the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum},
we have
\[
\expval{\mathbf{O}}_{\bar{\mu}}\stackrel{\textrm{Lemma }\ref{lemma:real-expectation-value-between-classical-quantum}}{=}\int X\rmd\bar{\mu}'\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu'\right\} \stackrel{\textrm{Lemma }\ref{lemma:interval-expectation-value-between-classical-quantum}}{=}\left\{ \expval{\mathbf{O}}_{\rho}\right\} \textrm{ ,}
\]
where $\mu'=\mul[\prime]=\mur[\prime]$.\end{proof}

\subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability
Measures}

After we defined the expectation value, we can provide another proof
of corollary~\ref{cor:Kochen-Specker-IVPM} which doesn't refer the
Kochen-Specker theorem directly. Assume there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
we will prove $\bar{\mu}$ has such bizarre properties that it cannot
exist. These properties will be summarized in the following two lemmas.

\begin{lemma}For any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
$\expval{\mathbf{O}}_{\bar{\mu}}$ is a singleton set~$\left\{ \lambda\right\} $,
where $\lambda$ is an eigenvalue of $\mathbf{O}$.\end{lemma}

\begin{proof}Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum}.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures called $\mu:\events\rightarrow\left\{ 1,0\right\} $.
By lemma~\ref{lemma:expectation-singleton}, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.
Since $\mu$ is a probability measure, there is only one pair of $\left(s_{0},i_{0}\right)$
such that $\mu\left(P_{i_{0}}^{s_{0}}\right)=1$. Therefore, 
\[
\expval{\mathbf{O}}_{\rho}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\textrm{ .}
\]
\end{proof}

@@

\begin{proof}\end{proof}
